Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-01-31 inst/examples/20170125-Manuscript-FK.Rmd
ok

dfs <- df %>% select(publication_year, publisher) %>% unique
p <- plot_timeline(dfs, x = "publication_year") +
     ylab("Publisher count (n)") + ggtitle(paste("Publisher count: ", cat, "/", myplace))
print(p)

kable(dfs)
```

>>>>

dfs <- df %>% select(publication_year, publisher) %>%
	      filter(!is.na(publisher)) %>%
              unique %>%	      
	      arrange(publication_year)
p <- plot_timeline(dfs, x = "publication_year", time.window = 1) +
       ylab("Publisher count (n)") +
       ggtitle(paste("Publisher count: ", cat, "/", myplace))
print(p)
kable(dfs)
.```
